---
title: "Supplementary data for the manuscript on the Pyrenodesmia Syngameon. Part I"
author: "Fernando Fernández Mendoza et al."
output:
  html_document: 
    keep_md: yes
    toc: true
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
  pdf_document: 
    keep_tex: yes
    toc: true
    number_sections: true
    toc_depth: 3
---

# Introduction

This document contains the suppelementary material necessary for the interpretation of the main manuscript regarding the taxonomically complex genus Pyrenodesmia. The supplement is organized in three parts.

The first part deals with population genetics and phylogenetic methods and aims at discussing the extent to which different methodological approaches can be used to identify species in this genus.

The second part uses sequences of the Mating type idiomorphs found in dykariotic samples to identify the extent to which there is a missmatch between postzigotic and prezygotic reproductive isolation.

Finally the third part surveys genomic signatures of hybridization encountered in the genome of Pyrenodesmia erodens.

The R code used for data processing, as untidy as it may be is shown together with the results. Some parts of the code have been commented out and substituted by importing a final environment to avoid repeating costly computations while compiling the supplement.

# Part I. Population and phylogenetic structure

## I.I Estimation of evolutionary populations in BAPS

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
load("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v15.Rdata")
#load("/Users/Fernando/Desktop/01_Sanger_paper/14_bGMYC_All_loci/03_Processed/workspace_step3.Rdata")

library(ggplot2)
library(reshape2)
library(fpc)
library(vcd)
library(ape)
library(phangorn)
library(bipartite)
library(knitr)
library(dplyr)

colorinos.bipolar<-c("#CAB2D6",
                     "#A6CEE3",
                     "#999999",
                     "#6A3D9A",
                     "#339933",
                     "#E31A1C",
                     "#FF7F00",
                     "#1F78B4",
                     "#B2DF8A",
                     "#FB9A99",
                     "#720D0E")
#
#
# Take out samples 810,811 Americanas and correct 281 and 357
#
#baps.adm["281",c(3,4,5,6)]<-baps.adm["1111",c(3,4,5,6)]
#baps.adm["357",c(3,4,5,6)]<-baps.adm["355",c(3,4,5,6)]
#baps.adm["194",c(3,4,5,6)]<-baps.adm["192",c(3,4,5,6)]
#baps.adm["261",c(3,4,5,6)]<-baps.adm["259",c(3,4,5,6)]
#baps.adm["262",c(3,4,5,6)]<-baps.adm["259",c(3,4,5,6)]
#baps.adm["318",c(3,4,5,6)]<-baps.adm["317",c(3,4,5,6)]
#baps.adm["318",2]<-baps.adm["17",2]
#baps.adm["283",2]<-baps.adm["17",2]
#baps.adm["178",2]<-baps.adm["17",2]
#baps.adm["1181",2]<-baps.adm["17",2]
#baps.adm["5",c(3,4,5,6)]<-baps.adm["3",c(3,4,5,6)]
#baps.adm["5.1",c(3,4,5,6)]<-baps.adm["3",c(3,4,5,6)]
#baps.adm["439",c(3,4,5,6)]<-baps.adm["438",c(3,4,5,6)]
#baps.adm["753",c(3,4,5,6)]<-baps.adm["751",c(3,4,5,6)]   
#baps.adm["753.1",c(3,4,5,6)]<-baps.adm["751",c(3,4,5,6)] 
#baps.adm["792",c(3,4,5,6)]<-baps.adm["794",c(3,4,5,6)]   
#baps.adm["792.1",c(3,4,5,6)]<-baps.adm["794",c(3,4,5,6)] 
#baps.adm["364",c(3,4,5,6)]<-baps.adm["854",c(3,4,5,6)]
#save.image("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v12.Rdata")
#
# Did not trim
#
#baps.adm<-baps.adm[rownames(baps.adm)!="810",]
#baps.adm<-baps.adm[rownames(baps.adm)!="811",]
#
# Last edit, ID correction
#
#a<-read.table("/Users/Fernando/Desktop/01_paper_sanger_drive/reidentify.txt",header=FALSE,sep="\t")
#rownames(a)<-a[,1]
#baps.adm$Species<-a[as.character(sapply(strsplit(rownames(baps.adm),"\\."),`[`,1)),2]
#baps.adm["1049",3:6]<-c(439,6.465392,45.991996,1755)
#save.image("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v13.Rdata")

#

sample_names<-sapply(strsplit(rownames(baps.adm),"\\."),`[`,1)
condensed_baps_adm<-baps.adm[!duplicated(sample_names),]
foo<-aggregate(x=baps.adm[,13:22],by=list(sample_names),FUN=mean)
rownames(foo)<-foo$Group.1
condensed_baps_adm[,13:22]<-foo[rownames(condensed_baps_adm),-1]
condensed_baps_adm<-cbind(sample=rownames(condensed_baps_adm),condensed_baps_adm)
condensed_baps_adm$name<-apply(condensed_baps_adm[,14:23],1,FUN=which.max)

orden.foo<-rownames(condensed_baps_adm)[order(condensed_baps_adm$name,-condensed_baps_adm$X1,-condensed_baps_adm$X2,-condensed_baps_adm$X3,-condensed_baps_adm$X4,-condensed_baps_adm$X5,-condensed_baps_adm$X6,-condensed_baps_adm$X7,-condensed_baps_adm$X8,-condensed_baps_adm$X9,-condensed_baps_adm$X10,condensed_baps_adm$sample)]

foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo)
foo<-melt(foo[,c(1,15:24)])
```


```{r}
#### Rarefaction curves

draw_haplo<-function(x)
  {
require(future.apply)
plan(multicore,workers=100)
foo<-x
foo<-foo[row.names(foo)!="Xanpa",]
foo.list<-seq(from=5,to=dim(foo)[1],by=50)
salida<-future_lapply(foo.list,FUN=function(z){
  sapply(c(1:100),FUN=function(y){
    mean(
      dist(
        foo[sample(1:dim(foo)[1],size=z),]
  )
)
}
)
})
return(melt(salida))
}

#fer<-draw_haplo(seq.dataset[[1]])
```
### Supplementary Figure 0. Species distribution in the dataset

```{r plot_sps1}
species_foo<-condensed_baps_adm[orden.foo,]
species_foo<-cbind(orden=factor(c(1:dim(species_foo)[1])),species_foo)
species_foo<-melt(species_foo[,c(1,3)])


p<-ggplot(species_foo) +
  geom_bar(aes(x=orden, y=1,fill=Species),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar) +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.25, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.5, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.75, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar()
print(p+theme(legend.position = "none"))
```

```{r plot_sps2}
legend <- cowplot::get_legend(p)
grid.newpage()
grid.draw(legend)
```
```{r plot_sps3, fig.width=10, fig.height=14}
print(p+theme(legend.position = "none")+facet_wrap(vars(Species)))
```

### Supplementary Figure 1. Differential contribution to admixture of each gene-pool.

```{r plot_baps}

p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=value,fill=variable),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar) +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.25, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.5, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 0.75, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
```

### Supplementary Figure 2. Contribution of each genepool to the minoritary admixed fractions.

```{r}
library(dplyr)
min_fract<-melt(condensed_baps_adm[,c(1,14:23)])
foo<-sum(min_fract$value)
min_fract %>% group_by(variable) %>% arrange(value,.by_group = TRUE) %>% summarize(Sum = sum(value, na.rm=TRUE)/foo) ->total_contribution

min_fract %>% group_by(sample) %>% slice_max(.,order_by = value) -> max_fract
min_fract<-min_fract[min_fract$value!=0&min_fract$value!=1,]
#min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE)

min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE) %>% dplyr::slice(1:n()-1) %>% ggplot(.,aes(x=variable,y=value,fill=variable))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2)) 
```

### Supplementary Table 1. Additive Contribution of each genepool to the admixed signal.

```{r}
foo<-sum(min_fract$value)
min_fract %>% group_by(variable) %>% arrange(value,.by_group = TRUE) %>% summarize(Sum = sum(value, na.rm=TRUE)/foo) ->foo
table_admixture_anovas<-cbind(total=total_contribution,admix=foo$Sum)
kable(table_admixture_anovas)
```

### Supplementary Figure 3 (A-E). Contribution of each genepool to the minoritary admixed fractions. Added contribution of each component to the minor component vs fraction of the total contribution to ancestry of the whole dataset.

```{r}
plot(foo$Sum~total_contribution$Sum)
linear_model<-glm(foo$Sum~total_contribution$Sum)
plot(linear_model)
```

### Supplementary table 2. Contribution of each genepool to the minoritary admixed fractions.

```{r}
kable(anova(linear_model))
```

### Supplementary Figure 4. Contribution of each genepool to the minoritary admixed fractions.

```{r}
min_fract<-melt(condensed_baps_adm[,c(1,14:23)])
min_fract<-min_fract[min_fract$value>0.05&min_fract$value<0.95,]
min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE)

min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE) %>% dplyr::slice(1:n()-1) %>% ggplot(.,aes(x=variable,y=value,fill=variable))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2)) 
```

### Supplementary table 3. Contribution of each genepool to the minoritary admixed fractions.

```{r}
min_fract %>% group_by(variable) %>% summarize(Mean = mean(value, na.rm=TRUE), Sum = sum(value, na.rm=TRUE)) %>% cbind(.,Max=as.numeric(table(max_fract$variable))) -> foo

foo %>% glm(Mean~Max,data=.) %>% anova %>% kable ()

table_admixture_anovas<-cbind(table_admixture_anovas,Mean05=foo$Mean,Sum05=foo$Sum,Max05=foo$Max)
```

### Supplementary table 4. Analisis of variance.

```{r}
foo %>% lm(Sum~Max,data=.) %>% anova %>% kable()
```

### Supplementary Figure 5. Contribution of each genepool to the minoritary admixed fractions considering at least 0.1 as a significant fraction.

```{r}
min_fract<-melt(condensed_baps_adm[,c(1,14:23)])
min_fract<-min_fract[min_fract$value>0.10&min_fract$value<0.90,]
min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE)

min_fract %>% group_by(sample) %>% arrange(value,.by_group = TRUE) %>% dplyr::slice(1:n()-1) %>% ggplot(.,aes(x=variable,y=value,fill=variable))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2)) 
```

### Supplementary table 5. Analisis of variance using average assignments

```{r}
min_fract %>% group_by(variable) %>% summarize(Mean = mean(value, na.rm=TRUE), Sum = sum(value, na.rm=TRUE)) %>% cbind(.,Max=as.numeric(table(max_fract$variable))) -> foo

foo %>% lm(Mean~Max,data=.) %>% anova
```

### Supplementary table 6. Analisis of variance using summed assignments.

```{r}
foo %>%  lm(Sum~Max,data=.) %>% anova
```

### Supplementary table 7. Contribution of each gene-pool to the minor admixed component across the dataset.

```{r}
table_admixture_anovas<-cbind(table_admixture_anovas,Mean1=foo$Mean,Sum1=foo$Sum,Max1=foo$Max)
kable(table_admixture_anovas)
```

### Supplementary Figure 6.

```{r}
plot(table_admixture_anovas)
```

### Supplementary table 8.

```{r}
table_admixture_anovas %>% glm(Max05~total.Sum,data=.) %>% anova %>% kable ()
```

### Supplementary table 9.

```{r}
table_admixture_anovas %>% glm(Max1~total.Sum,data=.) %>% anova %>% kable ()
```

### Supplementary table 10.

```{r}
table_admixture_anovas %>% glm(Mean05~total.Sum,data=.) %>% anova %>% kable ()
```

```{r}
table_admixture_anovas %>% glm(Mean1~total.Sum,data=.) %>% anova %>% kable ()
```

```{r}
table_admixture_anovas %>% glm(Sum05~total.Sum,data=.) %>% anova %>% kable ()
```

```{r}
table_admixture_anovas %>% glm(Sum1~total.Sum,data=.) %>% anova %>% kable ()
```

```{r}
kable(anova(linear_model))
```

### Geographic distribution of BAPS gene-pools

#### Supplementary figure

```{r}
library("rnaturalearth")
library("rnaturalearthdata")

world <- ne_countries(scale = "medium", returnclass = "sf")
foo<-condensed_baps_adm[condensed_baps_adm$X1>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[1]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X2>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[2]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X3>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[3]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X4>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[4]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X5>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[5]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X6>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[6]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X7>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[7]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X8>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[8]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X9>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[9]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

```{r}
foo<-condensed_baps_adm[condensed_baps_adm$X10>0.5,]
ggplot(data = world) + 
  geom_sf() + 
  theme_bw() + 
  coord_sf(xlim = c(-15, 70),
           ylim = c(30, 65),
           expand = FALSE) +
  stat_density_2d(geom = "polygon",
                  data=foo[!duplicated(foo$Locality),],
                  mapping = aes(x=lon,y=lat,alpha = ..level..),
                  fill = colorinos.bipolar[10]) +
  expand_limits(x= c(-30, 70),
                y = c(30, 65)) +
  geom_point(data=foo,
             aes(x=lon,y=lat))
```

### Association between gene-pools and morphospecies

```{r assoc_baps}
# Heatmap 1 Species vs BAPS

foo_tabla<-melt(table(condensed_baps_adm$Species,condensed_baps_adm$name))
foo_tabla$value[foo_tabla$value==0]<-NA


  ggplot(foo_tabla,aes(x=Var2,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
    scale_fill_gradient2(low = "#FFFFFF",
  mid = colorinos.bipolar[7],
  high = colorinos.bipolar[6],
  midpoint = 20,
  space = "Lab",
  na.value = "#FFFFFF",
  guide = "colourbar",
  aesthetics = "fill"
) +
  coord_fixed() + theme_bw() 
```

```{r, fig.width=14, fig.height=14}
print(assoc(table(condensed_baps_adm$Species,condensed_baps_adm$name),shade=TRUE))
```

```{r}
assocstats(table(condensed_baps_adm$Species,condensed_baps_adm$name))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm$Species,condensed_baps_adm$name))
```

### How much of the species splitting is explained by the assignment to gene-pools?

```{r}
library(mda)
foo_fdas<-condensed_baps_adm[,c("Species","X1","X2","X3","X4","X5","X6","X7","X8","X9","X10")]
disc_clusters<-mda::fda(Species~X1+X2+X3+X4+X5+X6+X7+X8+X9+X10, foo_fdas)
print(disc_clusters)
```

```{r}
kable(coef(disc_clusters,foo_fdas))
```
## I.II Phylogenetic signal in BAPS clusters and species IDs

### Phylogenetic signal in BAPS clusters

```{r}
library(picante)
library(ape)
library(adephylo)
library(ade4)
library(phylobase)
library(geiger)
library(phytools)
library(future.apply)

foo_adm<-baps.adm
rownames(foo_adm)<-paste("X",gsub("\\.1","B",rownames(foo_adm)),sep="")
foo_adm<-rbind(foo_adm,XXanpa=0)
plan(multicore,workers=10)
#phylosig_final<-future_lapply(
#  c("X1","X2","X3","X4","X5","X6","X7","X8","X9","X10"),
#  FUN=function(GRUPO)
#  {
#  phylo_signal<-lapply(tree.dataset,
#       FUN=function(x){
#  groups_mix<-as.numeric(foo_adm[x$tip.label,GRUPO])
#  names(groups_mix)<-x$tip.label
#  foo_out<-phytools::phylosig(
#  root(
#    compute.brlen(x),
#    outgroup = "XXanpa",
#    node=NULL,
#    resolve.root = TRUE),
#  groups_mix, method="lambda", test=TRUE, nsim=999)
#  return(foo_out)
#})
#  return(phylo_signal)
#})
load("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v15.Rdata")
print(phylosig_final)
#save.image("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v14.Rdata")
```

### Migrate-n migration network between BAPS gene clusters

```{r}
library(igraph)
connectors<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network.txt",header = FALSE)
nodes<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network2.txt",header = FALSE)
nodes<-data.frame(nodes=as.character(nodes[,1]),theta=as.numeric(nodes[,2]))
connectors<-data.frame(from = as.character(connectors[,1]),to = as.character(connectors[,2]),weight = as.numeric(connectors[,3]))
foo_col<-colorinos.bipolar[c(10,7,6,9,5,8,2,4,1,11)]
names(foo_col)<-nodes$nodes
rownames(nodes)<-nodes$nodes
migrate_M<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)
```
```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 500*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/20,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```
```{r}
connectors$weight<-connectors$weight*nodes[connectors$to,"theta"]
connectors_backup<-connectors
connectors<-connectors[connectors$weight>=2,]

#foo_col[connectors$to]
migrate_2Ne<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)

#set_vertex_attr(migrate, "theta", index = V(migrate), value = 100*as.numeric(nodes[,2]))
```
```{r}
coords<-layout_(migrate_2Ne,
                in_circle())
curves<-mat.or.vec(ecount(migrate_2Ne),1)

paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep="")
curves[gsub("M_","",connectors[,1])!=gsub("M_","",connectors[,2])]<--0.1
curves[!(paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep=""))]<-0
plot(migrate_2Ne,
     vertex.size = 500*vertex_attr(migrate_2Ne,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_2Ne)],
     edge.curved=curves,
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```

```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 500*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```
```{r}
foo.table<-cbind(nodes,from=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$from==x])}),to=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$to==x])}))
kable(cbind(foo.table[,-1],balance=foo.table$to-foo.table$from))

#kable(
#  rbind(
#  c("M_2",
#      sum(connectors_backup$weight[connectors_backup$from=="M_2"&connectors_backup$to!="M_3"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_2"&connectors_backup$from!="M_3"])
#      ),
##      c("M_3",
#      sum(connectors_backup$weight[connectors_backup$from=="M_3"&connectors_backup$to!="M_2"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_3"&connectors_backup$from!="M_2"])
#      )
#  )
#)
```

### Migrate-n migration network between BAPS gene clusters using mat genes

#### HMG

```{r}
library(igraph)
connectors<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network_hmg2",header = FALSE)
nodes<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network_hmg",header = FALSE)
nodes<-data.frame(nodes=as.character(nodes[,1]),theta=as.numeric(nodes[,2]))
connectors<-data.frame(from = as.character(connectors[,1]),to = as.character(connectors[,2]),weight = as.numeric(connectors[,3]))
foo_col<-colorinos.bipolar[c(10,7,6,9,5,8,2,4,1,11)]
names(foo_col)<-nodes$nodes
rownames(nodes)<-nodes$nodes
migrate_M<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)
```

#### Complete network edges proportional to M

```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 100*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/10,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```

```{r}
connectors$weight<-connectors$weight*nodes[connectors$to,"theta"]
connectors_backup<-connectors
connectors<-connectors[connectors$weight>=2,]

#foo_col[connectors$to]
migrate_2Ne<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)

#set_vertex_attr(migrate, "theta", index = V(migrate), value = 100*as.numeric(nodes[,2]))
```

#### Reduced netwrok edges are 2Neu only connections above 2 migrants per generation are shown.

```{r}
coords<-layout_(migrate_2Ne,
                in_circle())
curves<-mat.or.vec(ecount(migrate_2Ne),1)

paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep="")
curves[gsub("M_","",connectors[,1])!=gsub("M_","",connectors[,2])]<--0.1
curves[!(paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep=""))]<-0
plot(migrate_2Ne,
     vertex.size = 100*vertex_attr(migrate_2Ne,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/10,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_2Ne)],
     edge.curved=curves,
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```

```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 100*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/10,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```
```{r}
foo.table<-cbind(nodes,from=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$from==x])}),to=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$to==x])}))
kable(cbind(foo.table[,-1],balance=foo.table$to-foo.table$from))

#kable(
#  rbind(
#  c("M_2",
#      sum(connectors_backup$weight[connectors_backup$from=="M_2"&connectors_backup$to!="M_3"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_2"&connectors_backup$from!="M_3"])
#      ),
##      c("M_3",
#      sum(connectors_backup$weight[connectors_backup$from=="M_3"&connectors_backup$to!="M_2"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_3"&connectors_backup$from!="M_2"])
#      )
#  )
#)
```

#### Alpha

```{r}
library(igraph)
connectors<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network_a2",header = FALSE)
nodes<-read.delim2("/Users/Fernando/Desktop/01_Sanger_paper/19_migrate-n/for_network_a",header = FALSE)
nodes<-data.frame(nodes=as.character(nodes[,1]),theta=as.numeric(nodes[,2]))
connectors<-data.frame(from = as.character(connectors[,1]),to = as.character(connectors[,2]),weight = as.numeric(connectors[,3]))
foo_col<-colorinos.bipolar[c(10,7,6,9,5,8,2,4,1,11)]
names(foo_col)<-nodes$nodes
rownames(nodes)<-nodes$nodes
migrate_M<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)
```

#### Complete network edges proportional to M

```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 50*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/50,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```

```{r}
connectors$weight<-connectors$weight*nodes[connectors$to,"theta"]
connectors_backup<-connectors
connectors<-connectors[connectors$weight>=2,]

#foo_col[connectors$to]
migrate_2Ne<-graph_from_data_frame(connectors, directed = TRUE, vertices = nodes)

#set_vertex_attr(migrate, "theta", index = V(migrate), value = 100*as.numeric(nodes[,2]))
```

#### Reduced netwrok edges are 2Neu only connections above 2 migrants per generation are shown.

```{r}
coords<-layout_(migrate_2Ne,
                in_circle())
curves<-mat.or.vec(ecount(migrate_2Ne),1)

paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep="")
curves[gsub("M_","",connectors[,1])!=gsub("M_","",connectors[,2])]<--0.1
curves[!(paste(connectors[,1],connectors[,2],sep="")%in%paste(connectors[,2],connectors[,1],sep=""))]<-0
```
```{r}
plot(migrate_2Ne,
     vertex.size = 50*vertex_attr(migrate_2Ne,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/100,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_2Ne)],
     edge.curved=curves,
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```

```{r}
coords<-layout_(migrate_M,
                in_circle())
plot(migrate_M,
     vertex.size = 50*vertex_attr(migrate_M,"theta"),
     edge.arrow.size = 0.5,
     edge.width = connectors$weight/100,
     edge.color = foo_col[connectors$from],
     vertex.color = foo_col[V(migrate_M)],
     edge.curved=seq(-0.3, 0.3, length = ecount(migrate_M)),
     layout = coords,
     vertex.label.font=2,
     vertex.label.color="gray40",
     vertex.label.cex=.5
     )
```
```{r}
foo.table<-cbind(nodes,from=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$from==x])}),to=sapply(nodes[,1],FUN=function(x){sum(connectors_backup$weight[connectors_backup$to==x])}))
kable(cbind(foo.table[,-1],balance=foo.table$to-foo.table$from))

#kable(
#  rbind(
#  c("M_2",
#      sum(connectors_backup$weight[connectors_backup$from=="M_2"&connectors_backup$to!="M_3"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_2"&connectors_backup$from!="M_3"])
#      ),
##      c("M_3",
#      sum(connectors_backup$weight[connectors_backup$from=="M_3"&connectors_backup$to!="M_2"]),
#      sum(connectors_backup$weight[connectors_backup$to=="M_3"&connectors_backup$from!="M_2"])
#      )
#  )
#)
```


### Phylogenetic signal in Species IDs

```{r}
#load("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v14.Rdata")
#c(levels(factor(foo_adm$Species))[-1])
#plan(multicore,workers=12)
#phylosig_final2<-future_lapply(
#  levels(factor(foo_adm$Species))[-1],
#  FUN=function(GRUPO)
#  {
#  phylo_signal<-lapply(tree.dataset,
#       FUN=function(ARBOL)
#         {
#         foo_tree<-root(
#                  ARBOL,
#                  outgroup = "XXanpa",
#                  node=NULL,
#                  resolve.root = TRUE)
#        groups_mix<-as.numeric(factor(foo_adm[foo_tree$tip.label,"Species"])==GRUPO)
#        names(groups_mix)<-foo_tree$tip.label
   #     foo.out<-phytools::phylosig(
  #          compute.brlen(multi2di(foo_tree)),
 #           groups_mix, method="lambda", test=TRUE, nsim=100)
#        return(foo.out)
#})
#  return(phylo_signal)
#})
#names(phylosig_final2)<-levels(factor(foo_adm$Species))[-1]
#print(phylosig_final2)
#save.image("/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v15.Rdata")

fooeraseme<-melt(sapply(phylosig_final2,FUN=function(x){unlist(unlist(x)[c(1,6,11,16,21)])}))
colnames(fooeraseme)<-c("gene","sp","value")
ggplot(fooeraseme,aes(x=1,y=value,fill=sp))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2)) + facet_wrap(vars(sp)) + theme(legend.position = "none")
```
```{r}
ggplot(fooeraseme,aes(x=1,y=value,fill=gene))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2)) + facet_wrap(vars(gene)) + theme(legend.position = "none")
```

## I.III Concordance between gene phylogenies

### ML

The concordance between gene phylogenies was measured using Nye's similarity measurement (Nye 2000) implemented in r-package treedist. The trees were trimmed using function drop.tip to be made comparable and the number of shared The maximum concordance value was obtained as standarizing factor across loci, and trees with randomized tip assignments were used as random expectation.

```{r}
tree_similarity_fer<-function(x,y,reps=100)
{
  require(TreeDist)
  require(ape)
  foo.x<-keep.tip(x,x$tip.label[x$tip.label%in%y$tip.label])
  foo.y<-keep.tip(y,y$tip.label[y$tip.label%in%x$tip.label])
  foo.max<-NyeSimilarity(foo.x,foo.x)
  foo.obs<-NyeSimilarity(foo.x,foo.y)
  foo.ran<-c(1:reps)
  foo.ran<-sapply(foo.ran,FUN=function(z){
  foo.y$tip.label<-sample(foo.y$tip.label)
   return(NyeSimilarity(foo.x,foo.y))
  })
  return(c(foo.max,foo.obs/foo.max,mean(foo.ran)/foo.max))
}

results_foo<-NULL
for (i in c(1:length(tree.dataset)))
{
  for (j in c(1:length(tree.dataset)))
{
    print(paste (i,j))
    if (i!=j)
    {
      results_foo<-rbind(results_foo,tree_similarity_fer(tree.dataset[[i]],tree.dataset[[j]],10))
    }
    }
}
print(t.test(results_foo[,2],results_foo[,3],paired = TRUE,alternative = "greater"))
print(t.test(results_foo[,2],results_foo[,3],alternative = "greater"))
```

### Bayesian. Concordance within loci

```{r}
results_foo<-NULL
control_foo<-cbind(
  sample(c(1:length(all.trees)),1500,replace=TRUE),
  sample(c(1:length(all.trees)),1500,replace=TRUE),
  sample(c(1:50),1500,replace=TRUE),
  sample(c(1:50),1500,replace=TRUE)
)

control_foo<-control_foo[paste(control_foo[,1],control_foo[,3])!=paste(control_foo[,2],control_foo[,4]),]

control_foo<-control_foo[!(paste(control_foo[,1],control_foo[,3],control_foo[,2],control_foo[,4])%in%paste(control_foo[,2],control_foo[,4],control_foo[,1],control_foo[,3])),]

control_foo<-control_foo[sample(c(1:dim(control_foo)[1]),1000),]

results_foo<-future_apply(control_foo,1,FUN=function(x){
  return(c(x[1],x[2],x[3],x[4],results_foo,tree_similarity_fer(all.trees[[x[1]]][[x[3]]],all.trees[[x[2]]][[x[4]]],1)))
  })

results_foo<-t(results_foo)
same_foo<-factor(results_foo[,1]==results_foo[,2])
levels(same_foo)<-c("Between","Within")
ggplot(data.frame(proportion=results_foo[,6],comparison=same_foo),aes(x=comparison,y=proportion,fill=comparison))+geom_violin(alpha=0.5)+geom_point(position = position_jitter(seed = 1, width = 0.2))


```

### Within and between loci

```{r}
print(t.test(results_foo[same_foo=="Between",6],results_foo[same_foo=="Within",6],alternative = "less"))
```

### Between loci, random vs observed

```{r}
print(t.test(results_foo[same_foo=="Between",6],results_foo[same_foo=="Between",7],alternative = "greater"))
```


## I.IV Multilocus summary of bGMYC delimitations

### Averaging coassignment matrices

```{r bgmyc1}
names.bGMYC<-c("its","bt","efa","mcm7","rpb1","alpha","hmg")
#
#
#
#
#
#
recast_probmat <- function (x)
  {
  class(x)<-NULL
  x<-x[rownames(x)!="Xanpa",colnames(x)!="Xanpa"]
  x<-melt(x)
  x$Var1<-gsub("[A-Z]","",x$Var1,perl=TRUE)
  x$Var2<-gsub("[A-Z]","",x$Var2,perl=TRUE)
  #x<-aggregate(value~Var1+Var2,data_bgmyc_all,FUN = combined_probability)
  return(acast(x,Var1~Var2,fun.aggregate = mean))
}


x1<-recast_probmat(output.bgmyc.1[[3]])
x2<-recast_probmat(output.bgmyc.2[[3]])
x3<-recast_probmat(output.bgmyc.3[[3]])
x4<-recast_probmat(output.bgmyc.4[[3]])
x5<-recast_probmat(output.bgmyc.5[[3]])

nombres_tabla<-c(rownames(x1), rownames(x2), rownames(x3), rownames(x4), rownames(x5))
nombres_tabla<-nombres_tabla[!duplicated(nombres_tabla)]
nombres_tabla<-nombres_tabla[order(as.numeric(nombres_tabla))]

data_bgmyc_all<-rbind(melt(x1),melt(x2),melt(x3),melt(x4),melt(x5))
data_bgmyc_all<-acast(data_bgmyc_all,Var1~Var2,fun.aggregate = mean)
```

### Extended range of K for kmedoids K=1:200

```{r bgmyc_200}
#coco<-pamk(1-data_bgmyc_all,1:200,diss=TRUE)
#cluster_solutions<-coco$crit
#plot(cluster_solutions)
```

```{r bgmyc_50}
coco<-pamk(1-data_bgmyc_all,1:50,diss=TRUE)
cluster_solutions<-coco$crit
plot(cluster_solutions)
```

```{r assoc_50}
# Manually reorder
foo_bgmyc_clusters<-coco$pamobject$clustering

assoc(table(as.numeric(foo_bgmyc_clusters),condensed_baps_adm[names(foo_bgmyc_clusters),"name"]), shade = TRUE)
```

### Reduced range of K values K=1:20

```{r bgmyc_20}
coco<-pamk(1-data_bgmyc_all,1:20,diss=TRUE)
cluster_solutions<-coco$crit
plot(cluster_solutions)
#save.image("/Users/Fernando/Desktop/01_Sanger_paper/14_bGMYC_All_loci/03_Processed/workspace_step5.Rdata")
```

```{r assoc_20}
# Manually reorder
foo_bgmyc_clusters<-coco$pamobject$clustering
foo_bgmyc_clusters<-factor(foo_bgmyc_clusters,levels = c(2,4,1,7,8,6,5,3))

assoc(table(as.numeric(foo_bgmyc_clusters),condensed_baps_adm[names(foo_bgmyc_clusters),"name"]), shade = TRUE)
```
```{r}
assocstats(table(as.numeric(foo_bgmyc_clusters),condensed_baps_adm[names(foo_bgmyc_clusters),"name"]))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(as.numeric(foo_bgmyc_clusters),condensed_baps_adm[names(foo_bgmyc_clusters),"name"]))
```

```{r Heatmap_bGMYC}

foo_tabla<-melt(table(as.numeric(foo_bgmyc_clusters),condensed_baps_adm[names(foo_bgmyc_clusters),"name"]))
foo_tabla$value[foo_tabla$value==0]<-NA


  ggplot(foo_tabla,aes(x=Var1,y=Var2,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
    scale_fill_gradient2(low = "#FFFFFF",
  mid = colorinos.bipolar[7],
  high = colorinos.bipolar[6],
  midpoint = 20,
  space = "Lab",
  na.value = "#FFFFFF",
  guide = "colourbar",
  aesthetics = "fill"
) +
  coord_fixed() + theme_bw() 
```

```{r hmbgmyc}
# Heatmap 2 Species vs bGMYC
  
foo_tabla<-melt(table(condensed_baps_adm[names(foo_bgmyc_clusters),"Species"],as.numeric(foo_bgmyc_clusters)))
foo_tabla$value[foo_tabla$value==0]<-NA


ggplot(foo_tabla,
       aes(x=Var2,y=Var1,fill=value)) +
  geom_tile(color = "black") + 
  geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
  mid = colorinos.bipolar[7],
  high = colorinos.bipolar[6],
  midpoint = 20,
  space = "Lab",
  na.value = "#FFFFFF",
  guide = "colourbar",
  aesthetics = "fill") +
  coord_fixed() +
  theme_bw() 
```
```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters),"Species"],as.numeric(foo_bgmyc_clusters)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters),"Species"],as.numeric(foo_bgmyc_clusters)))
```

```{r bGMYC_50_all}
foo_bgmyc_clusters<-foo_bgmyc_clusters[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = foo_bgmyc_clusters[orden.foo])
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
```


## Single locus bGMYC

### ITS

```{r its_10}
coco.its<-pamk(1-x1,2:10,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
#+ facet_wrap(vars(clusters)))
```

```{r its_100, fig.dim = c(12, 20)}
coco.its<-pamk(1-x1,2:100,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white", guide = "none") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(clusters)))
```

#### Association with BAPS

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with species

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with multilocus bGMYC

```{r}
assocstats(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
```

### Beta Tubulin

```{r bt1}
coco.its<-pamk(1-x2,2:10,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
#+ facet_wrap(vars(clusters)))
```

```{r bt_100, fig.dim = c(12, 20)}
coco.its<-pamk(1-x2,2:100,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white", guide = "none") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(clusters)))
```

#### Association with BAPS

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with species

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with multilocus bGMYC

```{r}
assocstats(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
```

### Elongation factor alpha

```{r efa_1}
coco.its<-pamk(1-x3,2:15,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
#+ facet_wrap(vars(clusters)))
```

```{r efa_100, fig.dim = c(12, 20)}
coco.its<-pamk(1-x3,2:15,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white", guide = "none") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(clusters)))
```

#### Association with BAPS

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with species

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with multilocus bGMYC

```{r}
assocstats(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
```

### MCM7

```{r mcm7_1}
coco.its<-pamk(1-x4,2:10,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
#+ facet_wrap(vars(clusters)))
```

```{r mcm7_100, fig.dim = c(12, 20)}
coco.its<-pamk(1-x4,2:100,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white", guide= "none") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(clusters)))
```

#### Association with BAPS

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with species

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with multilocus bGMYC

```{r}
assocstats(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
```

### RPB1

```{r rpb1_1}
coco.its<-pamk(1-x5,2:10,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
#+ facet_wrap(vars(clusters)))
```

```{r rpb1_100, fig.dim = c(12, 20)}
coco.its<-pamk(1-x5,2:100,diss=TRUE)
foo_bgmyc_clusters.its<-coco.its$pamobject$clustering
foo_bgmyc_clusters.its<-foo_bgmyc_clusters.its[rownames(condensed_baps_adm)]
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo,clusters = as.factor(foo_bgmyc_clusters.its[orden.foo]))
foo<-melt(foo[,c(1,26)])  
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=clusters),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos.bipolar, na.value="white", guide = "none") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(clusters)))
```

#### Association with BAPS

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"name"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with species

```{r}
assocstats(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[names(foo_bgmyc_clusters.its),"Species"],as.numeric(foo_bgmyc_clusters.its)))
```

#### Association with multilocus bGMYC

```{r}
assocstats(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(foo_bgmyc_clusters[names(foo_bgmyc_clusters.its)],as.numeric(foo_bgmyc_clusters.its)))
```

# Part II. Mating type coocurrence

## II.I Read data and CD-HIT

```{r mat1}
i=9
for (file in c(
		"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/alpha_v13_exons.fasta",
		"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/hmg_v13_Only_exons.fasta"
		))
		{
		sequences<-read.dna(file,format="fasta")
		seq.dataset[[i]]<-sequences
		names.dataset[[i]]<-strsplit(rownames(sequences),split="_")
		i<-i+1
		}
#	library(phangorn)
	i=11
	for (file in c(
		"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/alpha_v13_translation.fasta",
		"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/hmg_v13_shortened_translation.fasta"
		))
		{
		sequences<-read.aa(file,format="fasta")
		seq.dataset[[i]]<-sequences
		names.dataset[[i]]<-strsplit(names(sequences),split="_")
		i<-i+1
		}
```

```{r mat2}
for ( i in 9:12)
	{
	for (j in 1:length(names.dataset[[i]]))
	{
	names.dataset[[i]][[j]]<-names.dataset[[i]][[j]][1]
	}
	names.dataset[[i]]<-unlist(names.dataset[[i]])
	}
#alpha 
names.dataset[[9]][is.na(as.numeric(names.dataset[[9]]))]<-c("207","205")
names.dataset$alpha_tr<-gsub("X","",names.dataset$alpha_tr)
names.dataset[[11]][is.na(as.numeric(names.dataset[[11]]))]<-c("207","205")
#hmg_tr"
names.dataset$hmg_tr<-gsub("X","",names.dataset$hmg_tr)
#
#
#
rownames(seq.dataset$alpha)<-names.dataset$alpha
rownames(seq.dataset$hmg)<-names.dataset$hmg
names(seq.dataset$alpha_tr)<-names.dataset$alpha_tr
names(seq.dataset$hmg_tr)<-names.dataset$hmg_tr
#
names.dataset[[8]][names.dataset[[8]]=="00"]<-"0"
names.dataset[[9]][names.dataset[[9]]=="00"]<-"0"
#
# Renumber doubled from Vondrak
#
a<-as.character(seq(2,56,2))
b<-as.character(seq(1,55,2))
for (i in 9:length(names.dataset))
	{
		for (j in 1:28)
		{
			names.dataset[[i]][names.dataset[[i]]==a[j]]<-b[j]
		}
	}
rm(a,b)


reduced.dataset$alpha<-seq.dataset$alpha[names.dataset$alpha%in%rownames(dataset),]
reduced.dataset$hmg<-seq.dataset$hmg[names.dataset$hmg%in%rownames(dataset),]

reduced.dataset$alpha_tr<-subset(seq.dataset$alpha_tr,names(seq.dataset$alpha_tr)%in%names.dataset$alpha_tr[names.dataset$alpha_tr%in%rownames(dataset)])
reduced.dataset$hmg_tr<-subset(seq.dataset$hmg_tr,names(seq.dataset$hmg_tr)%in%names.dataset$hmg_tr[names.dataset$hmg_tr%in%rownames(dataset)])
```

```{r mat3}
#
# 5. Export alignment files
#------------------------------
#for (i in 9:(length(names.dataset)-2))
#{
#if (is.list(names.dataset[[i]])==TRUE)#
#	{
#	names(seq.dataset[[i]])<-names.dataset[[i]]
#	write.dna(seq.dataset[[i]][names.dataset[[i]]%in%rownames(dataset)],paste("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/Subset_",names(names.dataset)[i],".fasta",sep=""),format="fasta",nbcol=-1,colsep="")
#	} else
#		{
#		rownames(seq.dataset[[i]])<-names.dataset[[i]]
#		write.dna(seq.dataset[[i]][names.dataset[[i]]%in%rownames(dataset),],paste("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/Subset_",names(names.dataset)[i],".fasta",sep=""),format="fasta",nbcol=-1,colsep="")
#		}
#
#}
#
#
#
#
#
#
# Factor dataset for bipartite networks
#
alpha.haplo<-mat.or.vec(length(reduced.dataset$alpha_tr),2)
rownames(alpha.haplo)<-names(reduced.dataset$alpha_tr)
for (i in 1:dim(alpha.haplo)[1]) 
	{
	alpha.haplo[i,1]<-paste(as.vector(reduced.dataset$alpha_tr)[[i]],collapse="")
	}
alpha.haplo<-alpha.haplo[!(rownames(alpha.haplo)%in%c("377","1073","1170","1171")),]
alpha.haplo[,2]<-factor(alpha.haplo[,1])

hmg.haplo<-mat.or.vec(length(reduced.dataset$hmg_tr),2)
rownames(hmg.haplo)<-names(reduced.dataset$hmg_tr)
for (i in 1:dim(hmg.haplo)[1]) 
	{
	hmg.haplo[i,1]<-paste(as.character(reduced.dataset$hmg_tr)[[i]],collapse="")
	}
hmg.haplo<-hmg.haplo[!(rownames(hmg.haplo)%in%c("377","1073","1170","1171")),]
hmg.haplo[,2]<-factor(hmg.haplo[,1])
#
#
#
foo.alpha<-as.character(sort(as.numeric(rownames(alpha.haplo))))[duplicated(as.character(sort(as.numeric(rownames(alpha.haplo)))))]
#
foo.hmg<-as.character(sort(as.numeric(rownames(hmg.haplo))))[duplicated(as.character(sort(as.numeric(rownames(hmg.haplo)))))]
foo.both<-c(foo.alpha,foo.hmg)
foo.both<-foo.both[!duplicated(foo.both)]
foo.both<-as.character(sort(as.numeric(foo.both)))
foo.names<-c(rownames(alpha.haplo),rownames(hmg.haplo))
foo.names<-as.character(sort(as.numeric(foo.names[!duplicated(foo.names)])))
#
#
out.haps<-NULL
for (i in foo.names)
	{
	if(i%in%rownames(alpha.haplo)&i%in%rownames(hmg.haplo))
	  {
	  a<-alpha.haplo[rownames(alpha.haplo)==i,2]
	  h<-hmg.haplo[rownames(hmg.haplo)==i,2]
	    for(j in a)
	     {
	      for (k in h)
	      {
	      out.haps<-rbind(out.haps,c(i,j,k))
	      }
	    }
	} else if (i%in%rownames(alpha.haplo)&!(i%in%rownames(hmg.haplo)))
	  {
	  a<-alpha.haplo[rownames(alpha.haplo)==i,2]
	  out.haps<-rbind(out.haps,cbind(i,a,0))
	  } else if (!(i%in%rownames(alpha.haplo))&i%in%rownames(hmg.haplo))
      {
	    a<-hmg.haplo[rownames(hmg.haplo)==i,2]
	    out.haps<-rbind(out.haps,cbind(i,0,a))
	    }
	}
	rownames(out.haps)<-out.haps[,1]
#
#
# 4. External Esport for clustering in CD-Hit
#
#alpha.haplo.seq<-as.character(newnames.reduced.dataset$alpha_tr)
#alpha.haplo.seq<-subset(alpha.haplo.seq,!duplicated(alpha.haplo[,2]))
#rownames(alpha.haplo.seq)<-paste("SeqID",alpha.haplo[!duplicated(alpha.haplo[,2]),2],"_",table(alpha.haplo[,2])[as.numeric(alpha.haplo[!duplicated(alpha.haplo[,2]),2])],sep="")
#alpha.haplo.seq<-alpha.haplo.seq[order(table(alpha.haplo[,2])[as.numeric(alpha.haplo[!duplicated(alpha.haplo[,2]),2])],decreasing=T),]

#hmg.haplo.seq<-as.character(newnames.reduced.dataset$hmg_tr)
#hmg.haplo.seq<-subset(hmg.haplo.seq,!duplicated(hmg.haplo[,2]))
#rownames(hmg.haplo.seq)<-paste("SeqID",hmg.haplo[!duplicated(hmg.haplo[,2]),2],"_",table(hmg.haplo[,2])[as.numeric(hmg.haplo[!duplicated(hmg.haplo[,2]),2])],sep="")
#hmg.haplo.seq<-hmg.haplo.seq[order(table(hmg.haplo[,2])[as.numeric(hmg.haplo[!duplicated(hmg.haplo[,2]),2])],decreasing=T),]

#write.aa(alpha.haplo.seq,"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/alpha_collapsed.fasta")
#write.aa(hmg.haplo.seq,"/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/hmg_collapsed.fasta")
#
# Import CD HIT
#
import.cd.hit<-function(file,reference)
{
require(stringr)
foo.read<-readLines(file)
foo.alpha99<-list()
a<-grep(">Cluster ",foo.read);
a<-c(a,length(foo.read))
for (i in 1:(length(a)-1))
	{
			if((a[i]+1)==(a[i+1]-1))
			{
				foo.alpha99[[i]]<-foo.read[(a[i]+1)]
			}
			else
				{
					foo.alpha99[[i]]<-foo.read[(a[i]+1):(a[i+1]-1)]
				}
			}
	names(foo.alpha99)<-foo.read[a[-length(a)]]
	for (i in 1:length(foo.alpha99)) foo.alpha99[[i]]<-str_extract(foo.alpha99[[i]], ">SeqID[0-9]+")
	for (i in 1:length(foo.alpha99)) foo.alpha99[[i]]<-gsub(">SeqID","",foo.alpha99[[i]])
	names(foo.alpha99)<-gsub(">Cluster ","",names(foo.alpha99))
	out<-mat.or.vec(length(reference[,2]),1)
	for (i in 1:length(foo.alpha99))
	{out[reference[,2]%in%foo.alpha99[[i]]]<-names(foo.alpha99)[i]}
	out<-as.numeric(out)+1
	return(out)
}

alpha.haplo<-cbind(alpha.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/alpha99.clstr",alpha.haplo))
alpha.haplo<-cbind(alpha.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/alpha97.clstr",alpha.haplo))
alpha.haplo<-cbind(alpha.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/alpha95.clstr",alpha.haplo))

hmg.haplo<-cbind(hmg.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/hmg99.clstr",hmg.haplo))
hmg.haplo<-cbind(hmg.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/hmg97.clstr",hmg.haplo))
hmg.haplo<-cbind(hmg.haplo,import.cd.hit("/Users/Fernando/Desktop/01_Sanger_paper/6_Mating_types/proteins/hmg95.clstr",hmg.haplo))
```

```{r}
#
# 99%
#
out.99<-NULL
out.97<-NULL
out.95<-NULL

for (i in foo.names)
	{
	if(i%in%rownames(alpha.haplo)&i%in%rownames(hmg.haplo))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,3]
	h<-hmg.haplo[rownames(hmg.haplo)==i,3]
	for(j in a)
	{
	for (k in h)
	{
	out.99<-rbind(out.99,c(i,j,k))
	}
	}
	}
	if (i%in%rownames(alpha.haplo)&!(i%in%rownames(hmg.haplo)))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,3]
	out.99<-rbind(out.99,cbind(i,a,0))
	}
	else if (!(i%in%rownames(alpha.haplo))&i%in%rownames(hmg.haplo))
	{
	a<-hmg.haplo[rownames(hmg.haplo)==i,3]
	out.99<-rbind(out.99,cbind(i,0,a))
	}
	}
	rownames(out.99)<-out.99[,1]
	
out.99<-out.99[!(rownames(out.99)%in%c("199","377","1073","1170","1171")),]
#
# 97%
#
for (i in foo.names)
	{
	if(i%in%rownames(alpha.haplo)&i%in%rownames(hmg.haplo))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,4]
	h<-hmg.haplo[rownames(hmg.haplo)==i,4]
	for(j in a)
	{
	for (k in h)
	{
	out.97<-rbind(out.97,c(i,j,k))
	}
	}
	}
	if (i%in%rownames(alpha.haplo)&!(i%in%rownames(hmg.haplo)))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,4]
	out.97<-rbind(out.97,cbind(i,a,0))
	}
	else if (!(i%in%rownames(alpha.haplo))&i%in%rownames(hmg.haplo))
	{
	a<-hmg.haplo[rownames(hmg.haplo)==i,4]
	out.97<-rbind(out.97,cbind(i,0,a))
	}
	}
	rownames(out.97)<-out.97[,1]
	
out.97<-out.97[!(rownames(out.97)%in%c("199","377","1073","1170","1171")),]
#
# 95% Similarity
#
for (i in foo.names)
	{
	if(i%in%rownames(alpha.haplo)&i%in%rownames(hmg.haplo))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,5]
	h<-hmg.haplo[rownames(hmg.haplo)==i,5]
	for(j in a)
	{
	for (k in h)
	{
	out.95<-rbind(out.95,c(i,j,k))
	}
	}
	}
	if (i%in%rownames(alpha.haplo)&!(i%in%rownames(hmg.haplo)))
	{
	a<-alpha.haplo[rownames(alpha.haplo)==i,5]
	out.95<-rbind(out.95,cbind(i,a,0))
	}
	else if (!(i%in%rownames(alpha.haplo))&i%in%rownames(hmg.haplo))
	{
	a<-hmg.haplo[rownames(hmg.haplo)==i,5]
	out.95<-rbind(out.95,cbind(i,0,a))
	}
	}
	rownames(out.95)<-out.95[,1]
	
out.95<-out.95[!(rownames(out.95)%in%c("199","377","1073","1170","1171")),]
```

## II.II Compartmentalization and modularity

### At haplotype level (Only compartments)

```{r}
table.mating.types<-out.haps[,-1]
table.mating.types<-table(table.mating.types[,1],table.mating.types[,2])
table.mating.types<-table.mating.types[-1,-1]
table.mating.types<-table.mating.types[rowSums(table.mating.types)>0,colSums(table.mating.types)>0]
comps<-compart(table.mating.types)
```

#### Network compartments

```{r compartments_haplotype_level}
colorinos_compartments<-colorRampPalette(colorinos.bipolar)(comps$n.compart)
plotweb(table.mating.types)
```
```{r}
kable(networklevel(table.mating.types))
```
```{r}
kable(grouplevel(table.mating.types))
```


### Comps vs species

### At 99% similarity level

```{r}
table.mating.types<-out.99[,-1]
table.mating.types<-table(table.mating.types[,1],table.mating.types[,2])
table.mating.types<-table.mating.types[-1,-1]
table.mating.types<-table.mating.types[rowSums(table.mating.types)>0,colSums(table.mating.types)>0]
comps<-compart(table.mating.types)
class(table.mating.types)<-NULL
cubo<-as.matrix(table.mating.types)
class(cubo)<-"matrix"
modules99<-metaComputeModules(cubo,N=5, steps=1e+05)
```

```{r compartments_99_level}
colorinos_compartments<-colorRampPalette(colorinos.bipolar)(comps$n.compart)
plotweb(modules99@moduleWeb,
        col.high = colorinos_compartments[(apply(comps$cweb,2,min)*-1)[colnames(modules99@moduleWeb)]],
        col.low =  colorinos_compartments[(apply(comps$cweb,1,min)*-1)[rownames(modules99@moduleWeb)]],
        bor.col.high = colorinos_compartments[(apply(comps$cweb,2,min)*-1)[colnames(modules99@moduleWeb)]],
        bor.col.low =  colorinos_compartments[(apply(comps$cweb,1,min)*-1)[rownames(modules99@moduleWeb)]],
        bor.col.interaction = 1, y.width.low =0.15, y.width.high = 0.15)
```

```{r modules_99_level}
foo1<-modules99@modules[-1,-c(1,2)]
foo2<-foo1[,(1+dim(modules99@originalWeb)[1]):dim(foo1)[2]]
foo1<-foo1[,1:dim(modules99@originalWeb)[1]]
foo1<-apply(foo1,2,FUN = function(x){which(x!=0)})
names(foo1)<-rownames(modules99@originalWeb)
foo2<-apply(foo2,2,FUN = function(x){which(x!=0)})
names(foo2)<-colnames(modules99@originalWeb)

colorinos_modules<-colorRampPalette(colorinos.bipolar)(dim(modules99@modules)[1]-1)

plotweb(modules99@moduleWeb,
        col.high = colorinos_modules[foo2[colnames(modules99@moduleWeb)]],
        col.low =  colorinos_modules[foo1[rownames(modules99@moduleWeb)]],
        bor.col.high = colorinos_modules[foo2[colnames(modules99@moduleWeb)]],
        bor.col.low =  colorinos_modules[foo1[rownames(modules99@moduleWeb)]],
        bor.col.interaction = 1, y.width.low =0.1, y.width.high = 0.1)
```

#### Donut plot compartments

```{r}
out.99.bckup<-out.99
out.99<-cbind(out.99,0,0,0)
out.99<-out.99[,-1]
colnames(out.99)<-c("alpha","hmg","compartments","modules1","modules2")

for (i in 1:length(rownames(out.99)))
	{
		if (out.99[i,1]!="0"&out.99[i,2]!="0")
		{
		out.99[i,3]<-comps$cweb[out.99[i,1],out.99[i,2]]	
			}
		else if (out.99[i,1]!="0"&out.99[i,1]%in%rownames(comps$cweb))
		{
		out.99[i,3]<-min(as.numeric(comps$cweb[out.99[i,1],]))
		}
		else if (out.99[i,2]!="0"&out.99[i,2]%in%colnames(comps$cweb))
		{
		out.99[i,3]<-min(as.numeric(comps$cweb[,out.99[i,2]]))
		}	
}
out.99[,4]<-foo1[as.character(out.99[,1])]
out.99[,5]<-foo1[as.character(out.99[,2])]



#out.99[is.na(out.99[,4]),4]<-foo2[as.character(out.99[,2])][is.na(out.99[,4])]
out.99[,3]<-as.numeric(out.99[,3])*-1
out.99[,4]<-as.numeric(out.99[,4])
out.99[,5]<-as.numeric(out.99[,5])
#
#
rownames(out.99)[duplicated(rownames(out.99))]<-paste(rownames(out.99)[duplicated(rownames(out.99))],".1",sep="")
rownames(out.99)[duplicated(rownames(out.99))]<-gsub("\\.1","\\.2",rownames(out.99)[duplicated(rownames(out.99))])
rownames(out.99)[duplicated(rownames(out.99))]<-gsub("\\.2","\\.3",rownames(out.99)[duplicated(rownames(out.99))])
rownames(out.99)[duplicated(rownames(out.99))]<-gsub("\\.3","\\.4",rownames(out.99)[duplicated(rownames(out.99))])
#
```

```{r}
foo_modules<-mat.or.vec(length(orden.foo),3)
rownames(foo_modules)<-orden.foo
colnames(foo_modules)<-colnames(out.99)[3:5]
foo_reduced<-out.99[rownames(out.99)%in%orden.foo,3:5]
foo_modules[rownames(foo_reduced),]<-foo_reduced
rm(foo_reduced)
#
#
#
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo, foo_modules[orden.foo,])
foo<-melt(foo[,c(1,26)]) 
foo$compartments[foo$compartments==0]<-NA
foo$compartments<-factor(foo$compartments,levels=1:comps$n.compart)
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=compartments),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos_compartments,na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
```

```{r}
print(p + facet_wrap(vars((compartments!=1|is.na(compartments)))))
```

#### Donut plots Modules

```{r}
foo<-condensed_baps_adm[orden.foo,]
foo<-cbind(orden=factor(c(1:dim(foo)[1])),foo, foo_modules[orden.foo,])
foo<-melt(foo[,c(1,28)]) 
foo$modules2[foo$modules2==0]<-NA
foo$modules2<-factor(foo$modules2,levels=names(table(foo$modules2))[order(as.numeric(table(foo$modules2)),decreasing=TRUE)])
  p<-ggplot(foo) +
  geom_bar(aes(x=orden, y=1,fill=modules2),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos_modules,na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
   geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + coord_polar() 
print(p)
```

```{r}
print(p + facet_wrap(vars(modules2)))
```
```{r}
kable(networklevel(table.mating.types))
```
```{r}
kable(grouplevel(table.mating.types))
```

```{r}
#save.image('/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v16final.Rdata')
```

```{r}
# Heatmap 3 Species vs modules
  
foo_tabla<-melt(table(condensed_baps_adm[as.character(rownames(foo)),2],foo$modules))
foo_tabla$value[foo_tabla$value==0]<-NA


  ggplot(foo_tabla,aes(x=Var2,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
    scale_fill_gradient2(low = "#FFFFFF",
  mid = colorinos.bipolar[7],
  high = colorinos.bipolar[6],
  midpoint = 20,
  space = "Lab",
  na.value = "#FFFFFF",
  guide = "colourbar",
  aesthetics = "fill"
) +
  coord_fixed() + theme_bw()   
```

```{r}
write.table(cbind(condensed_baps_adm,foo_bgmyc_clusters[rownames(condensed_baps_adm)],out.99[rownames(condensed_baps_adm)]),"/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_ferdi.txt")
```

## II.III Networks at individual level

```{r}
library(reshape2)
library(ggplot2)
library(fpc)
library(igraph)
library(robin)
library(scales)
#
# Create network of 99% similarity sequence clusters 
#
network_indivs<-mat.or.vec(length(rownames(out.99)[!duplicated(rownames(out.99))]),length(rownames(out.99)[!duplicated(rownames(out.99))]))
rownames(network_indivs)<-rownames(out.99)[!duplicated(rownames(out.99))]
colnames(network_indivs)<-rownames(out.99)[!duplicated(rownames(out.99))]
names_foo_network<-sapply(strsplit(rownames(out.99),"\\."),`[`,1)                        
for (foo.levels in levels(factor(out.99[,1]))[-1])
{
  foo_select<-names_foo_network[out.99[,1]==foo.levels]
  network_indivs[foo_select,foo_select]<-1
}
for (foo.levels in levels(factor(out.99[,2]))[-1])
{
  foo_select<-names_foo_network[out.99[,2]==foo.levels]
  network_indivs[foo_select,foo_select]<-network_indivs[foo_select,foo_select]+1
}
rownames(network_indivs)<-paste("s",rownames(network_indivs),sep="_")
colnames(network_indivs)<-paste("s",colnames(network_indivs),sep="_")
network_indivs<-network_indivs[!(rowSums(network_indivs)==diag(network_indivs)),!(rowSums(network_indivs)==diag(network_indivs))]
network_indivs[network_indivs==2]<-1
network_indivs[network_indivs==3]<-1
uni_graph<-igraph::graph_from_adjacency_matrix(network_indivs, mode ="undirected",diag=FALSE)
```

### Compartmentalization

```{r}
#
# Components
#
components<-igraph::components(uni_graph)
#
# Communities
#
communities_mat<-igraph::communities(components)
#
# Plot Graph with BAPS assignments
#
plot.igraph(uni_graph,layout=layout_with_fr(uni_graph),vertex.size=2, edge.arrow.size=0.2)
```

### Test modularity algorythms

```{r}

uni_graph2<-prepGraph(file=uni_graph, file.format="igraph")
attributes<-vertex_attr(uni_graph2, index = V(uni_graph2))
set.seed(10)
VI_In<-list()
comp<-list()
for (DA in c("walktrap", "louvain", "labelProp", "infomap"))
{
  members_In <- membershipCommunities(graph=uni_graph, method=DA)
  VI_In[[DA]] <- compare(components$membership, members_In, method="vi")
  for (DA1 in c("walktrap", "louvain", "labelProp", "infomap"))
  {
    if(DA!=DA1) {
      comp[[paste(DA,DA1,sep="_")]]<-robinCompare(graph=uni_graph2,method1 = DA, method2 = DA1, measure = "vi",type = "independent")
    }
  }  
}
for (i in 1:length(comp))
  {
  comp_foo<-comp[[i]]
  foo_bar1<-sapply(strsplit(names(comp)[i],"_"),`[`,1)
  foo_bar2<-sapply(strsplit(names(comp)[i],"_"),`[`,2)
  print(plotRobin(uni_graph2, model1=comp_foo$Mean1, model2=comp_foo$Mean2, legend = c(foo_bar1,foo_bar2), 
                  title = "Robin plot comparison based on VI"))
}
```

### Model selection based on BF

#### Simple random model

```{r}
graphRandomCM <- random(graph=uni_graph2)
proc_CM<-list()
for (DA in c("walktrap", "louvain", "labelProp", "infomap"))
{
  proc_CM[[DA]] <- robinRobust(graph=uni_graph2, graphRandom=graphRandomCM,
                       measure="vi", method=DA, type="independent")
}

for (i in 1:length(proc_CM))
{
  comp_foo<-proc_CM[[i]]
  print(plotRobin(uni_graph2, model1=comp_foo$Mean, model2=comp_foo$MeanRandom, legend = c(names(proc_CM)[i],"Null"), 
                  title = "Robin plot robustness based on VI"))
}
#
#
#
results_Robin<-mat.or.vec(length(proc_CM),4)
rownames(results_Robin)<-names(proc_CM)
colnames(results_Robin)<-c("bf_cm","auc_cm","bf_dk","auc_dk")
for (i in 1:length(proc_CM))
{
  results_Robin[i,1] <- robinGPTest(model1=proc_CM[[i]]$Mean, model2=proc_CM[[i]]$MeanRandom)
AUC <- robinAUC(graph=uni_graph2, model1=proc_CM[[i]]$Mean,
                model2=proc_CM[[i]]$MeanRandom)
results_Robin[i,2] <- AUC$area2/AUC$area1
robinFDATest(graph=uni_graph2, model1=proc_CM[[i]]$Mean, model2=proc_CM[[i]]$MeanRandom)
}
```

#### Random model based on dk-series

```{r}
#
# Complex random model dk-series
#
#write_graph(
#  uni_graph2,
#  "/Users/Fernando/Desktop/01_paper_sanger_drive/export_graph",
#  format = "edgelist")
#save.image('/Users/Fernando/Desktop/01_Sanger_paper/improvement_dataset.Rdata')
save.image('/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v17final.Rdata')

graphRandomDK <- prepGraph(file="/Users/Fernando/Desktop/01_paper_sanger_drive/dk2.1_export_graph",
                           file.format = "edgelist")
proc_DK<-list()
for (DA in c("walktrap", "louvain", "labelProp", "infomap"))
{
  proc_DK[[DA]] <- robinRobust(graph=uni_graph2, graphRandom=graphRandomDK,
                               measure="vi", method=DA, type="independent")
}
for (i in 1:length(proc_DK))
{
  comp_foo<-proc_DK[[i]]
  print(plotRobin(uni_graph2, model1=comp_foo$Mean, model2=comp_foo$MeanRandom, legend = c(names(proc_CM)[i],"Null"), 
                  title = "Robin plot robustness based on VI"))
}
```

```{r}
#
#
#
for (i in 1:length(proc_DK))
{
  results_Robin[i,3] <- robinGPTest(model1=proc_DK[[i]]$Mean, model2=proc_DK[[i]]$MeanRandom)
  AUC <- robinAUC(graph=uni_graph2,
                  model1=proc_DK[[i]]$Mean,
                  model2=proc_DK[[i]]$MeanRandom)
  results_Robin[i,4] <- AUC$area2/AUC$area1
  robinFDATest(graph=uni_graph2, model1=proc_DK[[i]]$Mean, model2=proc_DK[[i]]$MeanRandom)
}
```

```{r}
#save.image('/Users/Fernando/Desktop/01_Sanger_paper/improvement_dataset.Rdata')
#save.image('/Users/Fernando/Desktop/01_Sanger_paper/final_dataset_v18final.Rdata')
```

```{r}
#
# Modules
#
foo_comps<-membership(components)
names(foo_comps)<-sapply(strsplit(names(foo_comps),"_"),`[`,2)

#
#
foo<-condensed_baps_adm[orden.foo,]
foo<-data.frame(orden=factor(c(1:dim(foo)[1])),modules=factor(foo_comps[orden.foo],levels = order(table(foo_modules),decreasing=TRUE)))

colorinos_modules<-colorRampPalette(colorinos.bipolar)(max(foo_comps))


p<-ggplot(data.frame(foo)) +
  geom_bar(aes(x=orden, y=1,fill=modules),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos_modules,na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
                           axis.text.x=element_blank(),
                           axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                           axis.text.y=element_blank(),
                           axis.ticks.y=element_blank()) + coord_polar() 
print(p)
```

```{r}
print(p + facet_wrap(vars(modules!=1)))
```

```{r, fig.width=10, fig.height=10}
final_mods<-igraph::cluster_louvain(uni_graph2)
foo_modules<-membership(final_mods)
names(foo_modules)<-sapply(strsplit(names(foo_modules),"_"),`[`,2)

#
#
foo<-condensed_baps_adm[orden.foo,]
foo<-data.frame(orden=factor(c(1:dim(foo)[1])),modules=factor(foo_modules[orden.foo],levels = order(table(foo_modules),decreasing=TRUE)))

colorinos_modules<-colorRampPalette(colorinos.bipolar)(max(foo_modules))


p<-ggplot(data.frame(foo)) +
  geom_bar(aes(x=orden, y=1,fill=modules),
           stat="identity", alpha=0.5) +
  scale_fill_discrete(colorinos_modules,na.value="white") +
  geom_hline(yintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_hline(yintercept = 1, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 0, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 94, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 240, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 278, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 443, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 516, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 543, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 601, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 771, colour = 1, alpha=1, size=0.3) +
  geom_vline(xintercept = 806, colour = 1, alpha=1, size=0.3) +
  ylim(c(-0.5,1)) + 
  theme_linedraw() + theme(panel.grid.major.x = element_blank(),panel.grid.major.y = element_blank(),axis.title.x=element_blank(),
                           axis.text.x=element_blank(),
                           axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                           axis.text.y=element_blank(),
                           axis.ticks.y=element_blank()) + coord_polar() 
print(p + facet_wrap(vars(modules)))
```

```{r}
#
# Plot beyond to illustrate the networks
#
colorinos_neo<-hue_pal()(34)[c(1,12,20,10,9,3,7,23,11,24,4,5,14,6,2,13,21,8,18,25,26,19,15,22,16,27,28,17,29,30,31,32,33,34)]
color_clusters<-foo_modules
names(color_clusters)<-paste("s_",names(color_clusters),sep="")
color_clusters<-color_clusters[names(V(uni_graph2))]
plot(
  uni_graph2,
  vertex.size     = degree(uni_graph2)/10 +1,
  vertex.label    = NA,
  edge.arrow.size = .25,
  vertex.color    = colorinos_neo[color_clusters]
)
```

```{r}
foo<-induced_subgraph(uni_graph2,which(color_clusters%in%c(1,2,4,5,6,7,9,11,12,14,15,16,18)))
plot(
  foo,
  vertex.size     = degree(foo)/10 +1,
  vertex.label    = NA,
  edge.arrow.size = .25,
  vertex.color    = colorinos_neo[color_clusters[which(color_clusters%in%c(1,2,4,5,6,7,9,11,12,14,15,16,18))]]
)
```

```{r}
for (i in 1:34)
{
  plot(
    uni_graph2,
    vertex.size     = degree(uni_graph2)/10 +1,
    vertex.label    = NA,
    edge.arrow.size = .25,
    vertex.color    = color_clusters==i
  )
}
```

```{r}
stats_degree<-list()
stats_desc<-list()
stats_networks<-list()
for (i in 1:34)
  {
  foo<-induced_subgraph(uni_graph2,which(color_clusters==i))
  # Computing centrality measures for each vertex
  V(foo)$outdegree  <- degree(foo, mode = "out")
  V(foo)$closeness  <- closeness(foo, mode = "total", normalized = TRUE)
  V(foo)$betweeness <- betweenness(foo, normalized = TRUE)
  # Extracting each vectex features as a data.frame
  stats <- as_data_frame(foo, what = "vertices")
  stats_networks[[i]]<-stats
  # Computing quantiles for each variable
  stats_degree[[i]] <- with(stats, {
  cbind(
    outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
    closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
    betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
  )
})
  stats_desc[[i]] <- cbind(
    size    = vcount(foo),
    nedges  = ecount(foo),
    density = edge_density(foo),
    recip   = reciprocity(foo),
    centr   = centr_betw(foo)$centralization,
    pathLen = mean_distance(foo)
  )
}

foo<-induced_subgraph(uni_graph2,which(color_clusters%in%c(1,2,4,5,6,7,9,11,12,14,15,16,18)))
V(foo)$outdegree  <- degree(foo, mode = "out")
V(foo)$closeness  <- closeness(foo, mode = "total", normalized = TRUE)
V(foo)$betweeness <- betweenness(foo, normalized = TRUE)
stats <- as_data_frame(foo, what = "vertices")
stats_networks[[35]]<-stats
stats_degree[[35]] <- with(stats, {
  cbind(
    outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
    closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
    betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
  )
})
stats_desc[[35]] <- cbind(
  size    = vcount(foo),
  nedges  = ecount(foo),
  density = edge_density(foo),
  recip   = reciprocity(foo),
  centr   = centr_betw(foo)$centralization,
  pathLen = mean_distance(foo)
)

foo<-uni_graph2
V(foo)$outdegree  <- degree(foo, mode = "out")
V(foo)$closeness  <- closeness(foo, mode = "total", normalized = TRUE)
V(foo)$betweeness <- betweenness(foo, normalized = TRUE)
stats <- as_data_frame(foo, what = "vertices")
stats_networks[[36]]<-stats
stats_degree[[36]] <- with(stats, {
  cbind(
    outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
    closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
    betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
  )
})
stats_desc[[36]] <- cbind(
  size    = vcount(foo),
  nedges  = ecount(foo),
  density = edge_density(foo),
  recip   = reciprocity(foo),
  centr   = centr_betw(foo)$centralization,
  pathLen = mean_distance(foo)
)
stats_degree_trim<-stats_degree
stats_desc_trim<-stats_desc
```

```{r}
# Heatmap 3 Species vs modules
foo_tabla<-melt(table(condensed_baps_adm[as.character(names(foo_modules)),2],foo_modules))
foo_tabla$value[foo_tabla$value==0]<-NA


ggplot(foo_tabla,aes(x=foo_modules,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 20,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) +
  coord_fixed() + theme_bw()
#
#
#
```
```{r}


assocstats(table(condensed_baps_adm[as.character(names(foo_modules)),2],foo_modules))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(condensed_baps_adm[as.character(names(foo_modules)),2],foo_modules))
```

```{r}
geo_distances<-mat.or.vec(length(condensed_baps_adm[as.character(names(foo_modules)),2]),length(condensed_baps_adm[as.character(names(foo_modules)),2]))

for (X in 1:length(condensed_baps_adm[as.character(names(foo_modules)),2]))
{
  geo_distances[,X]<-geosphere::distGeo(cbind(as.numeric(condensed_baps_adm[as.character(names(foo_modules)),5]),as.numeric(condensed_baps_adm[as.character(names(foo_modules)),6]))[X,],cbind(as.numeric(condensed_baps_adm[as.character(names(foo_modules)),5]),as.numeric(condensed_baps_adm[as.character(names(foo_modules)),6])))
}

regions<-pamk(geo_distances,krange=2:10,diss=TRUE)

regions$pamobject$clustering

foo_tabla<-melt(table(regions$pamobject$clustering,foo_modules))
#foo_tabla$value[foo_tabla$value==0]<-NA


ggplot(foo_tabla,aes(x=foo_modules,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 20,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) +
  coord_fixed() + theme_bw()
```

```{r}


assocstats(table(regions$pamobject$clustering,foo_modules))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(regions$pamobject$clustering,foo_modules))
```

```{r, fig.width=10, fig.height=10}

foo_tabla<-melt(table(paste(condensed_baps_adm[as.character(names(foo_modules)),2],regions$pamobject$clustering),foo_modules))

ggplot(foo_tabla,aes(x=foo_modules,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 20,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) + coord_fixed() + theme_bw()

```
```{r}


assocstats(table(paste(condensed_baps_adm[as.character(names(foo_modules)),2],regions$pamobject$clustering),foo_modules))
#kable(chisq.residuals(table(condensed_baps_adm$Species,condensed_baps_adm$name)))

coindep_test(table(paste(condensed_baps_adm[as.character(names(foo_modules)),2],regions$pamobject$clustering),foo_modules))
```

```{r}
#
# Boxplots
#
i="all"
values<-cbind(i,degree(uni_graph2, mode = "out"),closeness(uni_graph2, mode = "total", normalized = TRUE),betweenness(uni_graph2, normalized = TRUE))
i="main"
foo<-induced_subgraph(uni_graph2,which(color_clusters%in%c(1,2,4,5,6,7,9,11,12,14,15,16,18)))
values<-rbind(values,cbind(i,degree(foo, mode = "out"),closeness(foo, mode = "total", normalized = TRUE),betweenness(foo, normalized = TRUE)))
for (i in c(1,2,4,5,6,7,9,11,12,14,15,16,18,3,8,10,13,17,19:34))
{
  foo<-induced_subgraph(uni_graph2,which(color_clusters==i))
  # Computing centrality measures for each vertex
values<-rbind(values,cbind(i,degree(foo, mode = "out"),closeness(foo, mode = "total", normalized = TRUE),betweenness(foo, normalized = TRUE)))
}
#colnames(values)<-c("group","degree","close","between")
values<-
  data.frame(group=factor(values[,1],
                          levels=c("all","main",1,2,4,5,6,7,9,11,12,14,15,16,18,3,8,10,13,17,19:34)),
             degree=as.numeric(values[,2]),close=as.numeric(values[,3]),between=as.numeric(values[,4]))
ggplot(values[values$group%in%c("all","main"),],aes(x=group,y=degree,fill=group))+geom_violin(alpha=0.5)
```
```{r}
ggplot(values,aes(x=group,y=degree,fill=group))+geom_violin(alpha=0.5,width=1.25)
```
```{r}
ggplot(values[values$group%in%c("all","main",1,2,4,5,6,7,9,11,12,14,15,16,18),],
       aes(x=group,y=degree,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}

#
ggplot(values[values$group%in%c("all","main"),],aes(x=group,y=close,fill=group))+geom_violin(alpha=0.5)
```
```{r}
ggplot(values,aes(x=group,y=close,fill=group))+geom_violin(alpha=0.5,width=1.25)
```
```{r}
ggplot(values[values$group%in%c("all","main",1,2,4,5,6,7,9,11,12,14,15,16,18),],
       aes(x=group,y=close,fill=group))+geom_violin(alpha=0.5,width=1.5)
values$close
```
```{r}
#
ggplot(values[values$group%in%c("all","main"),],aes(x=group,y=between,fill=group))+geom_violin(alpha=0.5)
```
```{r}
ggplot(values,aes(x=group,y=between,fill=group))+geom_violin(alpha=0.5,width=1.25)
```
```{r}
ggplot(values[values$group%in%c("all","main",1,2,4,5,6,7,9,11,12,14,15,16,18),],
       aes(x=group,y=between,fill=group))+geom_violin(alpha=0.5,width=1.5)
```

```{r}
#
#
#
#
# Cuantos grupos de closeness hay usando una mezcla de normales?
#
library(mclust)
V(uni_graph2)$outdegree  <- degree(uni_graph2, mode = "out")
V(uni_graph2)$closeness  <- closeness(uni_graph2, mode = "total", normalized = TRUE)
V(uni_graph2)$betweeness <- betweenness(uni_graph2, normalized = TRUE)
clustering_closeness<-Mclust(V(uni_graph2)$closeness)
plot(clustering_closeness)
table(clustering_closeness$classification)
```
```{r}
foo_tabla<-melt(table(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2],clustering_closeness$classification))
ggplot(foo_tabla,aes(x=Var2,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 33,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) + coord_fixed() + theme_bw()
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$closeness,group=factor(clustering_closeness$classification)),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$closeness,group=factor(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2])),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$closeness,group=factor(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),13])),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ferdframe<-data.frame(clo = V(uni_graph2)$closeness,group=factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)]))
ggplot(ferdframe,
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(1,2,4,5,6,7,9),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(11,12,14,15,18),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(16),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
#
# Betweenness
#
clustering_closeness<-Mclust(V(uni_graph2)$betweeness)
table(clustering_closeness$classification)
foo_tabla<-melt(table(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2],clustering_closeness$classification))
ggplot(foo_tabla,aes(x=Var2,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 40,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) + coord_fixed() + theme_bw()
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$betweeness,group=factor(clustering_closeness$classification)),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
#
#
ggplot(data.frame(clo = V(uni_graph2)$betweeness,group=factor(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2])),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$betweeness,group=factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)])),
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ferdframe<-data.frame(clo = V(uni_graph2)$betweeness,group=factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)]))
ggplot(ferdframe,
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(1,2,4,5,6,7,9),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(11,12,14,15,18),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(16),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```

```{r}
#

# Degree
#
clustering_closeness<-Mclust(V(uni_graph2)$outdegree)
table(clustering_closeness$classification)
foo_tabla<-melt(table(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2],clustering_closeness$classification))
ggplot(foo_tabla,aes(x=Var2,y=Var1,fill=value)) + geom_tile(color = "black") + geom_text(aes(label = value), color = "black", size = 2) +
  scale_fill_gradient2(low = "#FFFFFF",
                       mid = colorinos.bipolar[7],
                       high = colorinos.bipolar[6],
                       midpoint = 40,
                       space = "Lab",
                       na.value = "#FFFFFF",
                       guide = "colourbar",
                       aesthetics = "fill"
  ) + coord_fixed() + theme_bw()
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$outdegree,group=factor(clustering_closeness$classification)),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)+
  facet_wrap(vars(factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)])))
```
```{r}
#
#
ggplot(data.frame(clo = V(uni_graph2)$outdegree,group=factor(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),2])),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$outdegree,group=factor(condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),13])),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}

ferdframe<-data.frame(clo = V(uni_graph2)$outdegree,group=factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)]))

ggplot(ferdframe,
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(1,2,4,5,6,7,9),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(11,12,14,15,18),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
```
```{r}
ggplot(ferdframe[ferdframe$group%in%c(16),],
       aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1)
#
```
```{r}
V(uni_graph2)$closeness[condensed_baps_adm[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2),13]==1]
```
```{r}
#
# Not recalculate vertex stuff
#
stats_degree<-list()
stats_desc<-list()
V(uni_graph2)$outdegree  <- degree(uni_graph2, mode = "out")
V(uni_graph2)$closeness  <- closeness(uni_graph2, mode = "total", normalized = TRUE)
V(uni_graph2)$betweeness <- betweenness(uni_graph2, normalized = TRUE)
for (i in 1:34)
{
  foo<-induced_subgraph(uni_graph2,which(color_clusters==i))
  # Extracting each vectex features as a data.frame
  stats <- as_data_frame(foo, what = "vertices")
  # Computing quantiles for each variable
  stats_degree[[i]] <- with(stats, {
    cbind(
      outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
      closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
      betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
    )
  })
  stats_desc[[i]] <- cbind(
    size    = vcount(foo),
    nedges  = ecount(foo),
    density = edge_density(foo),
    recip   = reciprocity(foo),
    centr   = centr_betw(foo)$centralization,
    pathLen = mean_distance(foo)
  )
}

foo<-induced_subgraph(uni_graph2,which(color_clusters%in%c(1,2,4,5,6,7,9,11,12,14,15,16,18)))
stats <- as_data_frame(foo, what = "vertices")
stats_degree[[35]] <- with(stats, {
  cbind(
    outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
    closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
    betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
  )
})
stats_desc[[35]] <- cbind(
  size    = vcount(foo),
  nedges  = ecount(foo),
  density = edge_density(foo),
  recip   = reciprocity(foo),
  centr   = centr_betw(foo)$centralization,
  pathLen = mean_distance(foo)
)

foo<-uni_graph2
stats <- as_data_frame(foo, what = "vertices")
stats_degree[[36]] <- with(stats, {
  cbind(
    outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
    closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
    betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
  )
})
stats_desc[[36]] <- cbind(
  size    = vcount(foo),
  nedges  = ecount(foo),
  density = edge_density(foo),
  recip   = reciprocity(foo),
  centr   = centr_betw(foo)$centralization,
  pathLen = mean_distance(foo)
)
```
```{r}
print(stats_degree)
```
```{r}
print(stats_desc)
```
```{r}
stats_networksmelt<-melt(stats_networks)
library(stargazer)
for (i in c(1,2,4,5,6,7,9,11,12,14,15,16,18))
{
vertices_select<-stats_networksmelt[stats_networksmelt$L1==i,1]
foo<-stats_networksmelt[stats_networksmelt[,1]%in%vertices_select,]
print(ggplot(foo[foo$variable=="betweeness"&foo$L1!=35,],
              aes(x=factor(L1),y=value,z=variable,fill=factor(L1)))+geom_violin(alpha=0.5,width=1))
stargazer(anova(lm(value~factor(L1),data=foo[foo$variable=="betweeness"&foo$L1!=35,])),type = "text")
}

```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$outdegree,group=factor(clustering_closeness$classification)),aes(x=group,y=clo,fill=group))+geom_violin(alpha=0.5,width=1.5)+
facet_wrap(vars(factor(foo_modules[sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)])))
```
```{r}
ggplot(data.frame(clo = V(uni_graph2)$outdegree,group=factor(clustering_closeness$classification)),aes(x=group,y=clo,fill=group))+
  geom_violin(alpha=0.5,width=1.5)+
  facet_wrap(vars(factor(condensed_baps_adm[as.character(sapply(strsplit(names(V(uni_graph2)),"_"),`[`,2)),2])))
```


